Random Fibonacci Anyons Simulable via Covariant Action of Mapping Class Group

### 2014-08-26 ising/Fibonacci/about.tex
whack whack

@@

The mapping class group $MCG(D_n)$ acts on curve diagrams $f : L_n\to D_n$
via post-composition.

@@

See \cite{Kassel10} for more details on half-twists.

@@

\important{Problem:}
Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
find $\phi\in MCG(D_n)$ as a product of
a sequence of half-twists such that % DIAGRAM
$g = \phi f i,$ where $i$ is an inclusion of $L_2$ into $L_n:$

@@

@@

% DIAGRAM

@@

% DIAGRAM

let $h_k = g_k + f_k.$
This is a simple closed curve in $D$ which splits $D$
into two regions, the inside (simply connected) and the
outside.
We find six cases, which we can distinguish between
using the winding number and whether the end points
of $f$ are inside or outside:

% DIAGRAM

@@

\heading{Combinatorial formulation}

We discretize the prolem for software implementation...

@@

@@

\heading{Braid group representation}

\cite{Dehornoy02}

@@

\heading{Combinatorial Formulation}

\heading{Numerical Simulations}

>>>>

Every surface that is not a sphere, torus, disc or annulus, admits
a pair-of-pants decomposition, see \cite{Ivanov01}, Theorem 2.4.A.

@@

The mapping class group $MCG(D_n)$ acts on curve diagrams $f : L_n\to D_n$
via post-composition (left multiplication). See \cite{Dehornoy02}, chapter 6.

%\heading{Braid group representation}

In particular, we can single out specific ``braid'' elements of $MCG(D_n)$.
These act on the image of a pair-of-pants embedding: $g:D_2\to D_n.$

DIAGRAM

\heading{Half-twists}

@@

Each half-twist corresponds to a braid action of two neighbouring
holes on $f$.
See \cite{Kassel10}, Section 1.6.2, for more details on half-twists.

@@

\important{Problem:}
Given curve diagrams $f:L_n\to D_n$ and $g:L_2\to D_n$
find $\phi\in MCG(D_n)$ as a product of
a sequence of half-twists such that
$g = \phi f i,$ where $i$ is an inclusion of $L_2$ into $L_n:$

@@

The idea is that we would like to apply half-twists to a curve diagram
until the two holes indicated by $g$ become neighbours.

@@

\begin{center}
\includegraphics[width=0.3\textwidth]{snake-decompose.eps}
\end{center}

@@

\begin{center}
\includegraphics[width=0.3\textwidth]{snake-component.eps}
\end{center}

let $h_k = g_k + f_k.$
This is a simple closed curve in $D$ which splits $D$
into two regions, the inside (simply connected) and the
outside.
We find three basic cases (there are more including reflections
and rotations of these), which we can distinguish between
using the winding number and whether the end points
of $f$ are on the inside or outside of $h_k$:

\begin{center}
\includegraphics[width=0.5\textwidth]{snake-cases.eps}
\end{center}

@@

\heading{Disjoint sum of two curve diagrams}

Given two disjoint curve diagrams $f:L_m\to D_n$ and $f':L_{m'}\to D_n$
we define their sum  $f+f':L_{m+m'}\to D_n$ ...

\heading{Planar diagrams}

We aim discretize the problem for software implementation.
Our first task is to characterize what happens to a curve
if we ``forget'' any braiding inside a disc.
We define the following set of ``planar diagrams'' as:

    $$ T = \{ f(L)\cap E / \sim \ \text{s.t.}\ f:L\to D \}$$

where $f:L\to D$ is a curve (not an isotopy class)
whose image $f(L)$ intersects a disc $E\subset D$ in a finite number of components
and the equivalence relation $\sim$ consists of isotopies that fix $\partial E.$

This object has a simple combinatorial description 
as a string consisting of
the four labels {\bf ( ) H T} such that 
the parentheses are balanced. The two labels H and T specify the
head and tail endpoints of $f$, and each appears at most once in the string.

For example, the following diagram is represented by
the string {\bf(())H}:

\begin{center}
\includegraphics[width=0.5\textwidth]{planar.eps}
\end{center}

See \cite{Abramsky08} Proposition 1.6, for a similar treatment.

\heading{Tiling}

Now we consider a tiling of the disc into subdiscs that are disjoint on
their interiors.

\heading{Simulation and noise model}

@@

\begin{center}
\includegraphics[width=0.5\textwidth]{threshold-graph.eps}
\end{center}

@@

@@

%% ----------------------------------------------------------------------------
%
%\heading{Combinatorial Formulation}
%
%% ----------------------------------------------------------------------------
%
%\heading{Numerical Simulations}
